PLAE enables quick and easy searching across one million ocular transcriptomes

### 2022-07-17 manuscript_00.Rmd
updates

```{r}
# tic()
# ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)
# 
consist_diff2 <- scEiaD_2020_v01 %>%
  tbl("diff_testing") %>%
  filter(Base %in% ws_oct) %>%
  filter(Group == 'CellType (Predict)',
         Against == 'All',
         Organism %in% c('Homo sapiens','Mus musculus')) %>%
  group_by(Base, Gene) %>%
  summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-5), `mean padj` = mean(padj)) %>%
  filter(`mean log2FC` > 2, `sig count` > 1, `mean padj` < 1e-5) %>%
  collect() %>%
  mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>%
  left_join(gene_tab, by = 'GENEID') %>%
  relocate(SYMBOL, GENEID) %>%
  dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>%
  arrange(-`mean log2FC`)

@@

consist_diff %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n()) %>% ggplot(aes(x=`Base`, y = `Count` )) + geom_bar(stat='identity', position = 'dodge') + cowplot::theme_cowplot() + coord_flip() + xlab("CellType (Predict)")
#toc()
```

>>>>

```{r}
# tic()
# ws_oct <- ws_table %>% filter(`Well Supported` == 'Yes') %>% pull(`CellType (Predict)`)
# 
consist_diff3 <- scEiaD_2020_v01 %>%
  tbl("diff_testing") %>%
  filter(Base %in% ws_oct) %>%
  filter(Group == 'CellType (Predict)',
         Against == 'All',
         Organism %in% c('Homo sapiens','Mus musculus')) %>%
  group_by(Base, Gene) %>%
  summarise(`mean log2FC` = mean(log2FoldChange), `sig count` = sum(padj < 1e-5), `mean padj` = mean(padj)) %>%
  filter(`mean log2FC` > 4, `sig count` > 1, `mean padj` < 1e-5) %>%
  collect() %>%
  mutate(GENEID = str_extract(Gene, 'ENS\\w+')) %>%
  left_join(gene_tab, by = 'GENEID') %>%
  relocate(SYMBOL, GENEID) %>%
  dplyr::rename(Symbol = SYMBOL, ID = GENEID) %>%
  arrange(-`mean log2FC`)

@@

abc <- consist_diff3 %>% filter(Symbol %in% uniq_g$Symbol) %>% group_by(Base) %>% summarise(Count = n()) %>% ggplot(aes(x=`Base`, y = `Count` )) + geom_bar(stat='identity', position = 'dodge') + cowplot::theme_cowplot() + coord_flip() + xlab("CellType (Predict)")
#toc()
```
